Capturing subdiffusive solute dynamics and predicting long timescale selectivity in nanoscale pores with time series modeling

### 2020-01-12 Ben_Manuscripts/stochastic_transport/Final_Draft.tex
Added missing tex file

\usepackage{setspace}
\doublespacing
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

  \begin{abstract}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form:
  %MRS6: do you need the subscript for $\alpha$? makes it harder to read. 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  One can measure MSD in two ways. The time-averaged MSD measures all observed
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \end{equation}
  where T is the length of the trajectory. The ensemble averaged MSD measures
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. 
  % MRS6: does it correspond properly to the physical situation of entry into the 
  % pore of new particles at each unit time?
  % BJC6: no, but neither does ensemble
  Although theoretically possible, we do not use the ensemble averaged MSD to 
  calculate $\alpha$ because we can extract the same parameter with higher 
  precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. We cannot
  observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten  
  0.5 ns time lags of the 
  empirically measured autocorrelation function.

@@

  Assuming hops are correlated, solute behavior may be described by subordinated 
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
  The autocovariance function for FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This suggest two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. Solutes in mode 1 are in the pore region, defined
  %MRS4: some justification on why 0.75 vs. any other cutoff.
  %BJC4: I justified sentence after next. 
  as less than 0.75 nm from any pore center. All else are in mode 2, the tail region. 
  We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 1,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied between solutes due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations. 
  % BJC4: removed following sentence because I talk about aging above
  %The power law dwell time behavior gives rise to the aging phenomenon, embodied by a 
  %decrease in MSD with measurement time.~\cite{neusius_subdiffusion_2008,metzler_anomalous_2014}
  We reported the time-averaged MSD up to a 1000 ns time lag corresponding 95\% confidence
  intervals.

@@

  %BJC4: already said this earlier
%  We used a single Hurst parameter to describe
%  correlation between hops, independent of the solute's mode. Ideally, each mode
%  would have its own Hurst parameter, but we did not observe enough long sequences
%  of uninterrupted time spent in each mode with which to generate robust
%  autocorrelation functions.

  %BJC3: not sure how to cite fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
  validation of the approach).
  %MRS6: suggest in the supporting information describe what measure was used to determine that the algorithm sufficiently and reasonably approxmiates.

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, $T$,
  which describes the conditional probability of jumping to a specific state given
  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  %MRS6: maybe skip this next sentence since you don't actually use them?
%  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
%  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
%  dimensional reduction which are often necessary to identify representative states.

@@

  %MRS4: here, be more explicit you are testing the validity of the Markovian approximation on the molecular data.
  %BJC4: Tried to clarify in thesis statement. Let me know if you think it needs more
  We verified the Markovianity of state transitions by solutes in our MD simulations 
  by analyzing the empirically measured transition matrix. An important condition
  of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
  with time.~\cite{swope_describing_2004} We verified these properties 
  in Section~\ref{S-section:markov_validation} of the Supporting Information.

  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
  within each state as well as the dynamics of state transitions, which includes the
  overall configurational state of the solute and it's environments. 
  While MSMs are often used to estimate equilibrium populations of various states, adding 
  state-dependent dynamics allows us to simulate solute trajectories.
  %BJC5: I said the following earlier , but I still think it belongs
  Hence why we refer to them as Markov State-Dependent Dynamical Models (MSDDMs).

@@

  We determined the rate at which solutes cross macroscopic-length pores based on the
  Hill relation:~\cite{hill_free_1989}
  \begin{equation}
  J = \frac{1}{MFPT}
  \label{eqn:hill_relation}
  \end{equation}
  where $J$ is the single particle solute flux and MFPT refers to the mean first passage
  time. To account for input concentration dependence of the flux, assuming that particles
  are uncorrelated, one can multiply Equation~\ref{eqn:hill_relation} by the total number
  of particles to get the total flux. In the context of our work, the MFPT describes the
  average length of time it takes a particle to move from the pore entrance to the pore exit.

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
  realizations, released at the pore entrance ($z=0$). In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

  We calculated the expected value of analytical fits to the passage time distributions
  in order to determine the MFPT for a given solute and pore length. One should not 
  use the mean of the empirical passage time distribution because it is highly likely
  that the true MFPT will be underestimated unless 100\% of a very large number of 
  trajectories reach $L$. If a trajectory does not reach $L$ within $n$ steps, it is
  possible that a very long passage time has been excluded from the distribution.

@@

  %BJC4: Not sure if I should start by commenting on the stationarity of the 
  %solute trajectories. I talk about it when I start validating with the train/test procedure.

%  \subsection{Stationarity of Solute Trajectories}\label{section:stationarity}
%  %BJC4: Maybe re-theme the section: applicability of model
%  
%  Before applying the model, it is important to analyze the MD trajectories
%  themselves in order to understand what conclusions one could reasonably to 
%  draw by applying these models. 
%  
%  %BJC4: this might belong with validation.
%  We observe that in many cases, the distribution of solutes within the membrane
%  evolves slowly with time. We defined the perceived equilibration time point 
%  for each solute based on the time at which the number of solutes inside the
%  pores and tails stabilized. Nonetheless, we observe evidence of non-stationary
%  solute behavior after equilibration on the $\mu$s timescale. In Table \_\_, we compare the MSD of the 
%  solutes calculated using trajectory data from the first and second halves of the
%  equilibrated simulation time. Ethylene glycol and methanol, show considerable
%  differences in their MSDs. Although the MSD calculated from both halves of the 
%  acetic acid trajectories are similar, their shapes are considerably different 
%  (see SI). Urea is the only solute in this study that demonstrates satisfactory
%  stationarity on the 5 $\mu$s timescale.
%  
%  The non-stationary behavior of each solute presents itself in different ways.
%  On average, methanol molecules in the tails appear to be drifting further 
%  away from the pore center with time. Ethylene glycol appears to experience an
%  increased incidence of long trapping times. The partition of acetic acid 
%  between the pores and tails oscillates slowly over time. These problems probably
%  cannot be addressed without more simulation time or additional solute trajectories. 
%  
%  In light of these observations, we chose to demonstrate the performance and insights
%  that could be gained from our models using all of solutes with complete data sets
%  collected after the perceived equilibration time. However, we only use urea to 
%  validate the model's predictive power and to estimate solute flux.
%    
%  There are a couple of ways to address this issue in the long term. The simplest
%  approach is to run the MD simulations longer. This option is likely not feasible
%  because the equilibration timescale in these systems is unknown for most of 
%  the solutes in the study, even after consider computational effort. A more 
%  sustainable approach, which would help screen any solute of interest, would 
%  require us to learn the equilibrium distribution of solutes in the membrane

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:anticorrelated_hops}, we use urea to
  support this claim. Analogous figures for all other solutes are presented in the Supporting
  Information, Figures~\ref{S-fig:GCL_anticorrelated_hops}--\ref{S-fig:MET_anticorrelated_hops}.
  The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM or FLM because their analytical correlation 
  structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}). Fractional
  motion is common in crowded viscoelastic environments where movement is highly influenced by
  the movement of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  %The parameter estimates describing the 1 and 2 mode hop and dwell distributions are 
  %summarized in Figures~\ref{fig:1mode_parameters} and~\ref{fig:2mode_parameters}.

>>>>

\usepackage{setspace}
\doublespacing
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\newcommand{\colormap}{jet}  % colorbar to use
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

\usepackage{titlesec}
\titleformat{\subsubsection}[runin]
  {\normalfont\normalsize\bfseries}{\thesubsubsection}{1em}{}

@@

  %BJC6: I could make abstract margins smaller
  \begin{abstract}

@@

  Solutes in this system very clearly exhibit subdiffusive behavior, a type of
  anomalous diffusion. During an anomalous diffusion process, the mean squared 
  displacement (MSD) does not grow linearly with time, but instead it follows 
  a power law of the form: 
  \begin{equation} 
  \langle z^2(t) \rangle = K_{\alpha}t^{\alpha}
  \label{eqn:msd_form}
  \end{equation} 
  where $\alpha$ is the anomalous exponent and $K_{\alpha}$ is the generalized 
  diffusion coefficient. We only calculate MSD with respect to the solutes' center of
  mass $z$-coordinate, which is oriented along the pore axis. A value of $\alpha < 1$
  indicates a subdiffusive process, while values of $\alpha = 1$ and $\alpha > 1$ 
  are characteristic of Brownian and superdiffusive motion respectively.

@@

  One can measure MSD in two ways. The time-averaged MSD measures all observed
  displacements over time lag $\tau$: 
  \begin{equation}
  \overline{z^2(\tau)} = \dfrac{1}{T - \tau}\int_{0}^{T - \tau} (z(t + \tau) - z(t))^2 dt
  \label{eqn:tamsd}
  \end{equation}
  where T is the length of the trajectory. The ensemble averaged MSD measures
  displacements with respect to a particle's initial position:
  \begin{equation}
  \langle z^2(t) \rangle = \langle z(t) - z(0) \rangle^2
  \label{eqn:ensemble_msd}
  \end{equation}
  Fits to the \textit{ensemble} averaged MSD will always reproduce the form of 
  Equation~\ref{eqn:msd_form}.

@@

  We chose to analyze just the time-averaged MSD because, compared to the ensemble
  average, it is a more statistically robust measure of the average distance a 
  solute travels over time. Although theoretically possible, we do not use the 
  ensemble averaged MSD to calculate $\alpha$ because we can extract the same 
  parameter with higher precision using the dwell time distributions as described below.

@@

  \textit{Dwell time distributions:} For subdiffusive transport, the distribution 
  of dwell times is expected to fit a power law distribution 
  proportional to $t^{-1-\alpha}$.~\cite{meroz_toolbox_2015}
  Because we are limited to taking measurements at discrete intervals dictated by the output 
  frequency of our simulation trajectories, we fit the empirical dwell times
  to a discrete power law distribution whose maximum likelihood $\alpha$ 
  parameter we calculated by maximizing the likelihood function: 
  %BJC6: I could move these MLE equations to Supporting
  \begin{equation}
	\mathcal{L}(\beta) = -n\ln \zeta(\beta, t_{min}) -
	\beta\sum_{i=1}^{n} \ln t_i 
  \label{eqn:powerlaw_likelihood}
  \end{equation}
  where $\beta = 1 + \alpha$, $t_i$ are collected dwell time data points,
  $n$ the total number of data points, and $\zeta$ is the Hurwitz zeta function
  where $t_{min}$ is the smallest measured value of	$t$.~\cite{clauset_power-law_2009}

  In practical applications, the heavy tail of power law distributions can result in 
  arbitrarily long dwell times that are never observed in MD simulations. 
  %We cannot observe dwell times longer than the length of a single trajectory. 
  In order to directly compare our anomalous diffusion model to finite-length MD 
  trajectories we need to bound the dwell time distribution. We do this by adding 
  an exponential cut-off to the power law so the dwell time distribution is 
  now proportional to $t^{-1 - \alpha}e^{-\lambda t}$.
  %MRS6: are there papers to cite that this is a standard way to cut them off (i.e. rather than truncate, etc).
  % of the form:
%  \begin{equation}  %BJC3: maybe make this equation in line? Else move regular power law to its own equation
%    p(t) \propto t^{-1 - \alpha}e^{-\lambda t}
%  \label{eqn:powerlaw_cutoff}
%  \end{equation}
  We determine MLEs of $\alpha$ and $\lambda$ by maximizing the likelihood function:~\cite{clauset_power-law_2009}
  \begin{equation}
    \mathcal{L}(\alpha, \lambda) = n(1 - \alpha)\ln\lambda - n\ln\Gamma(1 - \alpha, t_{min}\lambda) - \alpha\sum_{i=1}^{n}\ln t_i - \lambda\sum_{i=1}^n t_i
  \label{eqn:powerlaw_cutoff_likelihood}
  \end{equation}

@@

  % BJC3: Making a logical argument regarding how we estimate H here is important
  % because I haven't seen anyone do it this way.
  sFBM implies that hops are correlated which we describe using the Hurst parameter, $H$. 
  The autocovariance function of hop lengths has the analytical form:~\cite{mandelbrot_fractional_1968}
  \begin{equation}
    \gamma(k) = \dfrac{\sigma^2}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg]
  \label{eqn:fbm_autocorrelation}
  \end{equation}
  where $\sigma^2$ is the variance of the underlying Gaussian distribution from which hops are
  drawn and $k$ is the time lag, or number of increments between hops. The hop autocorrelation
  function is simply Equation~\ref{eqn:fbm_autocorrelation} normalized by the variance. 
  When $H < 0.5$, hops are negatively correlated, when $H = 0.5$ we recover Brownian motion
  and when $H > 0.5$, one observes positive correlation between hops. 
  %BJC6: I could move the following to supporting and keep last sentence.
  There are many methods
  for estimating the Hurst parameter for a time series.~\cite{clegg_practical_2006} It can
  be a difficult task because Equation~\ref{eqn:fbm_autocorrelation} decays slowly to zero, 
  especially when $H > 0.5$, meaning one needs to study large time lags with high frequency.
  Fortunately (from a mathematical perspective), all of our solutes show anti-correlated motion, so most of the information in
  Equation~\ref{eqn:fbm_autocorrelation} is contained within the first few time lags (see 
  Figure~\ref{S-fig:hurst_autocorrelation} of the Supporting Information). Any hope of
  fitting longer time lags to our data is lost in the noise since the analytical values
  are so close to zero. Therefore, we obtained H by performing a least squares fit of 
  Equation~\ref{eqn:fbm_autocorrelation} to the first 
  ten  
  0.5 ns time lags of the 
  empirically measured autocorrelation function.

@@

  For correlated hops, solute behavior may be described by subordinated 
  fractional L\'evy motion (sFLM). The Hurst parameter can again be used to describe
  hop correlations because they share the same autocorrelation structure.~\cite{tikanmaki_fractional_2010}
  The autocovariance function for FLM is:
  \begin{equation}
    \gamma(k) = \dfrac{C}{2}\bigg[|k-1|^{2H} - 2|k|^{2H} + |k+1|^{2H}\bigg],
    ~C = \frac{E\big[L(1)^2\big]}{\Gamma(2H + 1)\sin(\pi H)}
    \label{eqn:flm_autocovariance}
  \end{equation}
  where $E\big[L(1)^2\big]$ is the expected value of squared draws from the 
  underlying L\'evy distribution, effectively the distribution's 
  variance.~\cite{bishwal_maximum_2011} In general, most L\'evy stable distributions
  have an undefined variance due to their heavy tails. However, normalizing
  Equation~\ref{eqn:flm_autocovariance} by the variance of a finite number of draws
  from a L\'evy stable distribution results in the same autocorrelation structure as FBM.
  See Section~\ref{S-section:H_estimate} of the Supporting Information for numerical
  simulations illustrating this point.  % BJC3: could use another reference proving mathematically what I show numerically

@@

  We observe different dynamical behavior when solutes move while inside 
  the pore versus while in the tail region. This suggest two anomalous diffusion 
  models of varying complexity. We created a simple, single mode model with a single 
  set of parameters fit to solute trajectories.
  Our second, two mode model assigns a set of parameters to each of 2 modes based
  on the solute's radial location. We define the first mode as the pore region, 
  defined as less than 0.75 nm from any pore center. All else are in the second mode, the
  tail region. We determined this cut-off by maximizing the difference in dynamical behavior as 
  described in our previous work.~\cite{coscia_chemically_2019} Unfortunately, 
  there were not enough sufficiently long sequences of hops in each mode to reliably
  calculate a Hurst parameter for each mode so we used the Hurst parameter from the 
  single mode model for both modes of the two mode model.

@@

  % BJC3: will need to modify this text to reflect different lengths of simulations
  For each solute, we simulated 1,000 anomalous diffusion trajectories of length
  $T_{sim}$ in order to directly compare our model's predictions to MD simulations.
  $T_{sim}$ varied between solutes due to differing solute equilibration times. We constructed 
  trajectories by simulating sequences of dwell times and correlated hop lengths
  generated based on parameters randomly chosen from our bootstrapped parameter 
  distributions. We propagated each trajectory until the total time equaled or 
  exceeded $T_{sim}~ \mu$s, then truncated the last data point so that the total 
  time exactly equaled $T_{sim}~ \mu$s since valid comparisons are only possible 
  between fixed length sFBM simulations.

  %BJC6: added this. Not sure how much detail is necessary
  We used Equation~\ref{eqn:tamsd} to calculate the time-averaged MSD of the MD
  and AD model trajectories then estimated their uncertainty using statistical 
  bootstrapping. For each bootstrap trial, we randomly chose $n$ solute trajectories,
  where $n$ is the number of independent trajectories, with replacement from the 
  ensemble of trajectories and then calculated the MSD of the subset. We reported 
  the time-averaged MSD up to a 1000 ns time lag with corresponding 95\% confidence
  intervals.

@@

  %BJC3: not sure how to cite fbm
  We used the Python package \texttt{fbm} to generate exact simulations of FBM and our
  own Python implementation of the algorithm by Stoev and Taqqu to simulate FLM.
  \cite{stoev_simulation_2004} Note that, to our knowledge, there are no known exact
  simulation algorithms for generating FLM trajectories. However, the algorithm
  we used sufficiently approximates draws from the marginal distribution and 
  reasonably approximates the correlation structure on MD simulation timescales. We
  added an empirical correction to enhance the accuracy of the correlation structure
  (see Section~\ref{S-section:flm_correlation} of the Supporting Information for 
  validation of the approach).
  % MRS6: suggest in the supporting information describe what measure was used to 
  % determine that the algorithm sufficiently and reasonably approxmiates.

@@

  A Markov state model (MSM) decomposes a time series into a set of discrete states
  with transitions between states defined by a transition probability matrix, $T$,
  which describes the conditional probability of moving to a specific state given
  the previously observed state.~\cite{pande_everything_2010,wehmeyer_introduction_2018}
  %MRS6: maybe skip this next sentence since you don't actually use them?
%  Software packages such as MSMbuilder~\cite{beauchamp_msmbuilder2:_2011} and 
%  pyEMMA~\cite{scherer_pyemma_2015} provide work flows capable of featurization and
%  dimensional reduction which are often necessary to identify representative states.

@@

  %BJC6: could defer most of this to supporting. 
  We verified the Markovianity of state transitions by solutes in our MD simulations 
  by analyzing the empirically measured transition matrix. An important condition
  of a Markov process is the satisfaction of detailed balance:
  \begin{equation}
  T_{i,j}P_i(t=\infty) = T_{j,i}P_j(t=\infty)
  \end{equation}
  where $P$ is the equilibrium distribution of states. In other words, the number of
  transitions from state $i$ to $j$ and from state $j$ to $i$ should be equal. A second
  test is to verify that $T$ holds up to coarser time scale partitioning. As long as solutes
  sufficiently sample the states in Table~\ref{table:states}, $T$ should be invariant
  with time.~\cite{swope_describing_2004} We verified these properties 
  in Section~\ref{S-section:markov_validation} of the Supporting Information.

  Adding to the standard MSM framework, we incorporated the dynamics of the solutes
  within each state as well as the dynamics of state transitions, which includes the
  overall configurational state of the solute and it's environments. 
  While MSMs are often used to estimate equilibrium populations of various states, adding 
  state-dependent dynamics allows us to simulate solute trajectories.
  %BJC5: I said the following earlier , but I still think it belongs
  Hence why we refer to them as Markov state-dependent dynamical models (MSDDMs).

@@

  We determined the rate at which solutes cross macroscopic-length pores based on the
  Hill relation:~\cite{hill_free_1989}
  \begin{equation}
  J = \frac{1}{MFPT}
  \label{eqn:hill_relation}
  \end{equation}
  where $J$ is the single particle solute flux and MFPT refers to the mean first passage
  time. To account for input concentration dependence of the flux, assuming that particles
  are independent, one can multiply Equation~\ref{eqn:hill_relation} by the total number
  of particles to get the total flux. In the context of our work, the MFPT describes the
  average length of time it takes a particle to move from the pore entrance to the pore exit.

  We generated particle trajectories, parameterized with the above models, in order
  to construct a distribution of first passage times across a membrane pore of length $L$.
  For computational reasons dependent on the model used, we simulated 1,000-10,000 trajectory
  realizations, released at the pore entrance ($z=0$). 
  %BJC6: next two sentences might not be necessary  
  In the case of 
  uncorrelated hops, one can continuously draw from the hop length distribution until 
  $z \geq L$ (or $-L$ for the sake of computational efficiency). The length of time 
  between the last time the particle crossed $z=0$ and the end of the trajectory gives a 
  single passage time. When particle hops are correlated, as they are in all cases of
  this work, we cannot continuously construct the particle trajectories. Rather, we must
  generate trajectories of length $n$ and measure the length of the sub-trajectory 
  which traverses from $0$ to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

  %BJC6: could probably remove this paragraph.
  We calculated the expected value of analytical fits to the passage time distributions
  in order to determine the MFPT for a given solute and pore length. One should not 
  use the mean of the empirical passage time distribution because it is highly likely
  that the true MFPT will be underestimated unless 100\% of a very large number of 
  trajectories reach $L$. If a trajectory does not reach $L$ within $n$ steps, it is
  possible that a very long passage time has been excluded from the distribution.

@@

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. In Figure~\ref{fig:solute_trajectories}, we plotted representative
  trajectories for each solute. They are characterized by intermittent hops between
  periods of entrapment. The near-Gaussian distribution of jump lengths and power law 
  distribution of dwell times are both characteristic of CTRWs 
  (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate 
  to the CTRW. We believe the subordinated process is FBM or FLM because their analytical
  correlation structures are close to those observed in our simulations (Figure~\ref{fig:hop_acf}).
  Fractional motion is common in crowded viscoelastic environments where movement is highly 
  influenced by the movement of surrounding components, such as monomer tails in our 
  case.~\cite{ernst_fractional_2012}
